Variational Inference for Inverse Reinforcement Learning with Gaussian Processes

### 2019-03-23 mpaper/paper.tex
Fancy evaluation plots: version 1

\documentclass{mpaper}
\usepackage{bm}
\usepackage{bbm}
\usepackage{mathtools}
\usepackage{thmtools, thm-restate}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{tikz}
\usepackage{layouts}
\usepackage{xcolor}
\usepackage{booktabs}

\usetikzlibrary{shapes,bayesnet,arrows.meta,arrows}
%\tikzstyle{myarrow} = [-{Latex[length=2mm,width=2mm]}]

@@

>>>>

\documentclass{mpaper}
\usepackage{bm}
\usepackage{bbm}
\usepackage{mathtools}
\usepackage{thmtools, thm-restate}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{tikz}
\usepackage{layouts}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{csvsimple}
\usepackage{pgfplots}

\usetikzlibrary{shapes,bayesnet,arrows.meta,arrows,calc,pgfplots.colormaps}
%\tikzstyle{myarrow} = [-{Latex[length=2mm,width=2mm]}]

@@

\begin{figure}
  \begin{tikzpicture}[
    /pgfplots/colormap/violet,
    ellipse2/.style={
      draw,
      ellipse,
      /utils/exec={
        \pgfplotscolormapdefinemappedcolor{#1}},
      fill=mapped color},
    edge2/.style={
      ultra thick,
      /utils/exec={
        \pgfplotscolormapdefinemappedcolor{#1}},
      draw=mapped color}]
    \csvreader[
    no head,
    column count=11
    ]{covariance_and_policy_transformed.csv}{1=\x, 2=\y, 3=\Soneone, 4=\Stwotwo, 5=\Sthreethree, 6=\Stwoone, 7=\Sthreeone, 8=\Sthreetwo, 9=\ponetwo, 10=\ptwoone, 11=\pthreetwo}{%
      \node[ellipse2=1000] (s1) at (3*\x, 2*\y) {$s_1$};
      \node[ellipse2=\Stwotwo] (s2) at (3*\x+1, 2*\y+1) {$s_2$};
      \node[ellipse2=\Sthreethree] (s3) at (3*\x+2, 2*\y) {$s_3$};
      \draw[edge2=\Stwoone] (s1) -- (s2);
      \draw[edge2=\Sthreeone] (s1) to (s3);
      \draw[edge2=\Sthreetwo] (s2) to (s3);
    }
    \draw [<->] (2.5, 5.5) node (yaxis) [above] {$\zeta_2$}
    |- (8.5, 1.5) node (xaxis) [right] {$\zeta_1$};
    \foreach \x in {1, 2} {
      \node (x\x) at (1+3*\x, 1.3) {$\x$};
    }
    \foreach \y in {1, 2} {
      \node (y\y) at (2.3, 0.5+2*\y) {$\y$};
    }
  \end{tikzpicture}
\end{figure}
